Evaluation of Cache-Oblivious Data Structures

### 2008-05-25 paper/paper.tex
-
Added and updated a bunch of scripts.
Added scaling of input to aggregation script (not very nice, but it works). Added/updated some plots.
Added some more figures to the paper (these will change later).

@@

\section{Results}
% Present results!
% Tables, graphs, etc.
% What to include:
%   per program:     transitions/states graph
%   per program/set: 
%
%

@@

>>>>

\begin{table}
\begin{center}
\begin{tabular}{ l l l l }
\hline
\textbf{Case} & \textbf{Parameters} & \textbf{Iterations} & \textbf{Transitions} \\
\hline
eratosthenes & $N=40$ & 1,019,960 & 4,923,218 \\
leader2 & $N=5$ & 5,950,945 & 23,856,363 \\
peterson\_N & \\
\hline
\end{tabular}
\caption{Properties of test cases used}
\label{tab-cases}
\end{center}
\end{table}

@@

\section{Results}

\begin{figure}
\centering
\includegraphics[width=83mm]{fig-eratosthenes-bender_wctime}
\caption{Eratosthenes/Bender set execution time}
\label{fig-eratosthenes-bender_wctime}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=83mm]{fig-eratosthenes-bender_vss}
\caption{Eratosthenes/Bender set memory usage}
\label{fig-eratosthenes-bender_vss}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=83mm]{fig-eratosthenes-hash_wctime}
\caption{Eratosthenes/hash table execution time}
\label{fig-eratosthenes-hash_wctime}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=83mm]{fig-eratosthenes-hash_vss}
\caption{Eratosthenes/hash table memory usage}
\label{fig-eratosthenes-hash_vss}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=83mm]{fig-eratosthenes-btree_wctime}
\caption{Eratosthenes/B-tree execution time}
\label{fig-eratosthenes-btree}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=83mm]{fig-eratosthenes-btree_vss}
\caption{Eratosthenes/B-tree memory usage}
\label{fig-eratosthenes-btree}
\end{figure}

% Present results!
% Tables, graphs, etc.
% What to include:
%   queue size over iterations
%       for each program
%
%   insertions per query:
%       for each program
%
%   per program:
%       wctime over iterations
%          for each set
%       memory over iterations
%          for each set
%

@@

\include{fig-queuesize}
